Diverse Genotype-by-Weather Interactions in Switchgrass

### 2024-05-21 manuscript/revision2/revision2.tex
revision: Add Section S1 to the SI Appendix

We next looked for evidence of GxWeather by jointly re-estimating
genetic effects across all eight common gardens using the mash model,
which can flexibly capture many modes of covariance across gardens
(Figure~\ref{fig-map} D; SI Appendix, Datasets 1-6). We specified three
qualitative categories of covariance structures across gardens:
``canonical'' covariance, with simple patterns of effect size covariance
introduced in the initial \emph{mash} manuscript; ``data-driven''
covariances derived from common patterns of SNP effects observed in the
data, and ``GxWeather'' covariance, estimated from the covariance of
empirical weather patterns at each garden at specific times before the
phenological event (Table 1; SI Appendix, Section S2). For example, the
more similar that the amount of rainfall prior to flowering is for
genotypes A and B between gardens in MI and MO, the nearer these
covariances will be to one. If rainfall amounts are uncorrelated,
covariance will be near zero; if there is rank changing (e.g.~high
rainfall before flowering of A at MO but not MI, and high rainfall
before flowering for B at MI but not MO), this covariance will be near
negative one. We specified multiple covariance structures for the
canonical, data-driven, and GxWeather categories, each of which
represented a specific pattern of covariance in genetic effect size
estimates that could be included in the model. The phenotypic
correlations for the timing of vegetative growth had moderate negative
correlations between the Texas and North gardens, particularly in the
Gulf subpopulation and Both subpopulations (Figure~\ref{fig-map} B). If
these phenotypic correlations have a genetic component, they could be
partially or completely captured by the covariance structures specified
in the mash model.

@@

We used a greedy algorithm to select covariance matrices from each
model's set that significantly improved the model likelihood. Five
GxWeather covariance structures were selected, zero to two per
subpopulation: two for green-up date, and three for flowering date. Of
these five, three had mass on them in mash models of the strong effects
(Figure~\ref{fig-covar} A-B). Two of these three matrices had negative
covariances between sites between Texas and North gardens
(Figure~\ref{fig-covar} A), while one had all positive or near-zero
covariances. SNP-associated phenotypic effects covaried with different
weather-based cues in the Gulf \& in Both subpopulations
(Figure~\ref{fig-covar} B). In total, 65\% of the posterior weight of
strong SNP effects in the mash model of Gulf green-up fell on a
covariance matrix constructed using the covariance of day length 14 days
prior to the date of green-up. The covariance matrix for this weather
cue was visually similar to the observed pattern of phenotypic
correlation for the timing of vegetative growth in the Gulf
subpopulation (Figure~\ref{fig-map} B; Figure~\ref{fig-covar} A). Mash
models of the timing of vegetative growth in the Midwest subpopulation
and Both subpopulations did not include this GxWeather covariance; the
Midwest had no weight on any GxWeather covariance, while Both
subpopulations had non-zero weights on two additional GxWeather
covariance types, average temperature one day prior to green-up, and the
day length change in seconds in the day prior to green-up
(Figure~\ref{fig-covar} B). The average temperature covariance matrix
had negative covariances between Texas and North gardens, though not as
strong as the negative phenotypic correlations seen in Both
subpopulations (Figure~\ref{fig-map} B; Figure~\ref{fig-covar} A). Only
the Gulf subpopulation and Both subpopulations had mass on any GxWeather
covariance matrices (Figure~\ref{fig-covar} C) for vegetative growth.

For flowering date, distinct GxWeather covariance structures captured
covariance in effect sizes for SNPs in the Gulf and Midwest
subpopulations. 33\% of SNP effects on flowering in the Gulf
subpopulation covaried with cumulative rainfall in the seven days prior
to flowering (Figure~\ref{fig-covar} D). 22.6\% of SNP effects on
flowering in the Midwest subpopulation covaried with day length change
in the two days prior to flowering (Figure~\ref{fig-covar} D), which had
negative covariances between Texas and North gardens. Neither of these
covariance matrices significantly improved the log-likelihood of the
\emph{mash} model of Both subpopulations, and no GxWeather covariance
matrices had non-zero mass in models of Both subpopulations
(Figure~\ref{fig-covar} E). In five of the six mash models of strong
effects, the GxWeather covariance matrices captured a minority of the
posterior weights of the strong effects (Figure~\ref{fig-covar} C,E); in
these five models, the majority of this mass was on various canonical
covariance matrices. These matrices included simple heterozygosity, with
intermediate, positive covariances between all gardens, and
garden-specific effects present only at one garden.

@@

We sought additional experimental support for our joint re-estimates of
SNP effects using an independent pseudo-F2 mapping population created
from Gulf \& Midwest individuals and grown at the same sites
(Figure~\ref{fig-qtl} A,B). We conducted quantitative trait loci (QTL)
mapping of flowering as functions of five environmental cues that we
also used as covariance matrices in mash, and identified eight QTL for
flowering date, eight QTL for flowering as a function of day length
change two days prior, one QTL for the start of vegetative growth, and
two QTL for vegetative growth as a function of daylength change one day
prior, all of which showed QTL by environment interactions (SI Appendix,
Fig. S3). All QTL for flowering overlapped one or more homologs from
rice or \emph{A. thaliana} with functionally validated roles in
flowering (SI Appendix, Dataset 7). All flowering and green-up QTL
intervals contained at least one SNP significant in at least one mash
run at a log10-transformed Bayes Factor \textgreater{} 2, or in the 1\%
tail of significance, whichever was stricter (SI Appendix, Dataset 8).
We also looked for enrichments of mash SNPs in the 1\% tail of
significance (the `mash 1\% tail') within each QTL interval. At the 5\%
level, three QTL had enrichments of SNPs in the mash 1\% tail. Overall,
there were five significant enrichments (p \textless{} 0.05,
hypergeometric test) of SNPs in the mash 1\% tail in the QTL intervals.
Thus, we were able to experimentally support some of our re-estimates of
SNP effects with a QTL mapping experiment using a separate mapping
population.

@@

\caption{\label{fig-map}Characterization of the timing of vegetative
(green-up) and reproductive (flowering) growth in the switchgrass
diversity panel. (a) Map and trait histograms of green-up and flowering
dates across two genetically distinct switchgrass subpopulations and
eight common gardens. Purple represents individuals from the Midwest
genetic subpopulation, and pink individuals from the Gulf subpopulation;
map positions represent the original collection locations for the
genotypes, and shapes represent the ecotype of the genotype. Vertical
dashed lines indicate the summer solstice. Common gardens are arranged
in latitudinal order. (b) Phenotypic correlations between clonal
replicates planted at eight common gardens, within and between two
genetic subpopulations. (c) Narrow sense heritability of green-up and
flowering within single common gardens (purple) and across all eight
common gardens (green), within and between two genetic subpopulations.
(d) Flow diagram of the methods applied to the green-up and flowering
dates to jointly estimate SNP effects across all sites. Mash was fit to
SNP effect data and used to find covariance matrices that improved the
mash model likelihood using a large set of randomly selected, relatively
unlinked SNP effects; this model was applied to a ``strong'' set of SNP
effects with large effect sizes in the univariate GWAS.}

@@

\caption{\label{fig-covar}Example hypothesis-driven covariance matrices
specified in mash and the posterior weights placed on all covariance
matrices. (a) Left column: Five example hypothesized covariance matrices
specified for the green-up date or flowering date phenotype; these
matrices were created from environment-specific correlations across
eight common gardens, and are described in Table 1. Common gardens are
arranged in latitudinal order within the matrices. Right column: Five
example canonical covariance matrices. Canonical matrices (purple) have
simple interpretations, such as equal effects across all common gardens,
or effects specific to a single common garden. (b,d) Total posterior
weight placed on each covariance matrix type specified for (b) green-up
date and (d) flowering date mash models, within and between two genetic
subpopulations. Hypothesized covariance matrices (green). Covariance
matrices included in mash that had zero posterior weight in all three
mash runs on the genetic subpopulations, such as the identity matrix,
are not shown. (c,e) Total posterior weight placed on covariance
matrices that were hypothesized or canonical, for the (c) green-up date
phenotype and (e) flowering date phenotype.}

@@

\caption{\label{fig-qtl}Overlaps of QTL from an outbred pseudo-F2 cross
and with jointly re-estimated SNP effects in the 1\% tail of
significance from a diversity panel. Dotted lines indicate
permutation-based significance thresholds for each weather-related
function. Stars indicate QTL with significant enrichment for SNPs in the
1\% mash tail; G, M, and B indicate which subpopulation had enrichment:
G - Gulf subpopulation, M -Midwest subpopulation, B - both
subpopulations. Rug plots show genomic locations of SNPs in the 1\% mash
tail for flowering date for each subpopulation. a) QTL mapping for the
start of vegetative growth (Greenup Date), and three weather-related
functions of greenup date. b) QTL mapping for the start of reproductive
growth (Flowering Date), and two weather-related functions of flowering
date.}

@@

The formation and resequencing of the diversity panel has been described
previously (33). The diversity panel contained 134 sequenced, clonally
propagated individuals from the Midwest genetic subpopulation, and 229
from the Gulf genetic subpopulation. To allow for the possibility that
different subpopulations had different strengths of connection between
our phenotypes and genotypes (41), we conducted three sets of genetic
analyses: on Gulf and Midwest genotypes separately, and on both
subpopulations together (`Both'). Analyses to determine narrow-sense
heritability (h\textsuperscript{2}) for green-up and flowering were done
using linear mixed models and followed (33). Details on these models can
be found in (SI Appendix, Section S3,S4).

@@

To evaluate the prevalence and kinds of covariance patterns of SNP
effects across our common gardens, we used multivariate adaptive
shrinkage (\emph{mash}) on SNP effect estimates from the diversity panel
(36). To do this, we first conducted univarate genome-wide association
(GWAS) on site-specific best linear unbiased predictors (BLUPs) for the
timing of vegetative growth and flowering, using the switchgrassGWAS
package and the methods in (40). We used the effect estimates for single
nucleotide polymorphisms (SNPs) from these GWAS as preliminary effect
estimates for the two traits at each garden. We then jointly modeled
genetic effect estimates, and the mixture of ways these effects might
covary, across all eight common gardens, using a two-part procedure. We
first modeled genetic effects with different combinations of covariance
structures, using the effect size estimates from a subset of \ul{19K}
relatively unlinked (r\textsuperscript{2} \textless{} 0.2), randomly
selected SNPs used in the GWAS. In these models (hereafter referred to
as ``random''), we then specified a variety of potential covariance
structures among genetic effect size estimates from each garden (as
expanded on below) and used a greedy algorithm to iteratively select and
add covariance structures that significantly improved the log likelihood
of the \emph{mash} model. Given the high correlation between some of the
covariance patterns we tested, this approach allowed us to select only
the subset of patterns of covariance that significantly improved the fit
of the jointly inferred structure of genetic effect estimates present in
the data. We then selected 19K relatively unlinked (r\textsuperscript{2}
\textless{} 0.2) SNPs from each univariate GWAS that had the largest
effect estimates in each GWAS (hereafter ``strong'' effects), which gave
sets of \ul{\textbf{48K - 80K}} SNPs, and jointly re-estimated these
effect size estimates at all eight sites using the set of significant
covariance matrices that most improved the model fit on the random
effects. Notably, the majority of these ``strong'' effects were not
significant in univariate GWAS.

We generated hypothesis-based covariance matrices derived from
correlations in environmental cues in the green-up or flowering date
windows for the three populations (Table 1; SI Appendix, Table S1,
Section S1). These covariance matrices represent correlations between
identical genotypes drawn from a specific population at pairs of common
gardens; covariances near one mean that the population has a strong,
positive linear relationship in individual responses at that pair of
gardens, while covariances near zero mean that there is no relationship
within the population for individual responses at that pair of gardens.
Mash SNP effects will undergo strong shrinkage towards one another in
the first case, and little shrinkage in the second case. Mash also
generates data-driven covariance matrices corresponding to major
patterns of SNP effects present in the data. We generated six
data-driven matrices per mash run, five produced by singular value
decomposition (SVD) of an overall matrix.

@@

To confirm candidate genomic regions and patterns of allelic effects
found in the diversity panel, we analyzed flowering in an outbred
pseudo-F2 cross between four individuals, two Midwest and two Gulf
individuals. The formation of this mapping population has been described
previously (35); additional details on QTL mapping can be found in SI
Appendix, Section S6. To be directly comparable to the diversity panel
data, only 2019 phenology data from the pseudo-F2 cross from the same
eight common garden sites were used.

>>>>

We next looked for evidence of GxWeather by jointly re-estimating
genetic effects across all eight common gardens using the \emph{mash}
model, which can flexibly capture many modes of covariance across
gardens (Figure~\ref{fig-map} D; SI Appendix, Datasets 1-6). We
specified three qualitative categories of covariance structures across
gardens: ``canonical'' covariance, with simple patterns of effect size
covariance introduced in the initial \emph{mash} manuscript;
``data-driven'' covariances derived from common patterns of SNP effects
observed in the data, and ``GxWeather'' covariance, estimated from the
covariance of empirical weather patterns at each garden at specific
times before the phenological event (Table 1; SI Appendix, Section S2).
For example, the more similar that the amount of rainfall prior to
flowering is for genotypes A and B between gardens in MI and MO, the
nearer these covariances will be to one. If rainfall amounts are
uncorrelated, covariance will be near zero; if there is rank changing
(e.g.~high rainfall before flowering of A at MO but not MI, and high
rainfall before flowering for B at MI but not MO), this covariance will
be near negative one. We specified multiple covariance structures for
the canonical, data-driven, and GxWeather categories, each of which
represented a specific pattern of covariance in genetic effect size
estimates that could be included in the model. The phenotypic
correlations for the timing of vegetative growth had moderate negative
correlations between the Texas and North gardens, particularly in the
Gulf subpopulation and Both subpopulations (Figure~\ref{fig-map} B). If
these phenotypic correlations have a genetic component, they could be
partially or completely captured by the covariance structures specified
in the \emph{mash} model.

@@

We used a greedy algorithm to select covariance matrices from each
model's set that significantly improved the model likelihood. Five
GxWeather covariance structures were selected, zero to two per
subpopulation: two for green-up date, and three for flowering date. Of
these five, three had mass on them in \emph{mash} models of the strong
effects (Figure~\ref{fig-covar} A-B). Two of these three matrices had
negative covariances between sites between Texas and North gardens
(Figure~\ref{fig-covar} A), while one had all positive or near-zero
covariances. SNP-associated phenotypic effects covaried with different
weather-based cues in the Gulf \& in Both subpopulations
(Figure~\ref{fig-covar} B). In total, 65\% of the posterior weight of
strong SNP effects in the \emph{mash} model of Gulf green-up fell on a
covariance matrix constructed using the covariance of day length 14 days
prior to the date of green-up. The covariance matrix for this weather
cue was visually similar to the observed pattern of phenotypic
correlation for the timing of vegetative growth in the Gulf
subpopulation (Figure~\ref{fig-map} B; Figure~\ref{fig-covar} A).
\emph{Mash} models of the timing of vegetative growth in the Midwest
subpopulation and Both subpopulations did not include this GxWeather
covariance; the Midwest had no weight on any GxWeather covariance, while
Both subpopulations had non-zero weights on two additional GxWeather
covariance types, average temperature one day prior to green-up, and the
day length change in seconds in the day prior to green-up
(Figure~\ref{fig-covar} B). The average temperature covariance matrix
had negative covariances between Texas and North gardens, though not as
strong as the negative phenotypic correlations seen in Both
subpopulations (Figure~\ref{fig-map} B; Figure~\ref{fig-covar} A). Only
the Gulf subpopulation and Both subpopulations had mass on any GxWeather
covariance matrices (Figure~\ref{fig-covar} C) for vegetative growth.

For flowering date, distinct GxWeather covariance structures captured
covariance in effect sizes for SNPs in the Gulf and Midwest
subpopulations. 33\% of SNP effects on flowering in the Gulf
subpopulation covaried with cumulative rainfall in the seven days prior
to flowering (Figure~\ref{fig-covar} D). 22.6\% of SNP effects on
flowering in the Midwest subpopulation covaried with day length change
in the two days prior to flowering (Figure~\ref{fig-covar} D), which had
negative covariances between Texas and North gardens. Neither of these
covariance matrices significantly improved the log-likelihood of the
\emph{mash} model of Both subpopulations, and no GxWeather covariance
matrices had non-zero mass in models of Both subpopulations
(Figure~\ref{fig-covar} E). In five of the six \emph{mash} models of
strong effects, the GxWeather covariance matrices captured a minority of
the posterior weights of the strong effects (Figure~\ref{fig-covar}
C,E); in these five models, the majority of this mass was on various
canonical covariance matrices. These matrices included simple
heterozygosity, with intermediate, positive covariances between all
gardens, and garden-specific effects present only at one garden.

@@

We sought additional experimental support for our joint re-estimates of
SNP effects using an independent pseudo-F2 mapping population created
from Gulf \& Midwest individuals and grown at the same sites
(Figure~\ref{fig-qtl} A,B). We conducted quantitative trait loci (QTL)
mapping of flowering as functions of five environmental cues that we
also used as covariance matrices in \emph{mash}, and identified eight
QTL for flowering date, eight QTL for flowering as a function of day
length change two days prior, one QTL for the start of vegetative
growth, and two QTL for vegetative growth as a function of daylength
change one day prior, all of which showed QTL by environment
interactions (SI Appendix, Fig. S3). All QTL for flowering overlapped
one or more homologs from rice or \emph{A. thaliana} with functionally
validated roles in flowering (SI Appendix, Dataset 7). All flowering and
green-up QTL intervals contained at least one SNP significant in at
least one \emph{mash} run at a log10-transformed Bayes Factor
\textgreater{} 2, or in the 1\% tail of significance, whichever was
stricter (SI Appendix, Dataset 8). We also looked for enrichments of
\emph{mash} SNPs in the 1\% tail of significance (the `\emph{mash} 1\%
tail') within each QTL interval. At the 5\% level, three QTL had
enrichments of SNPs in the \emph{mash} 1\% tail. Overall, there were
five significant enrichments (p \textless{} 0.05, hypergeometric test)
of SNPs in the \emph{mash} 1\% tail in the QTL intervals. Thus, we were
able to experimentally support some of our re-estimates of SNP effects
with a QTL mapping experiment using a separate mapping population.

@@

\caption{\label{fig-map}Characterization of the timing of vegetative
(green-up) and reproductive (flowering) growth in the switchgrass
diversity panel. (a) Map and trait histograms of green-up and flowering
dates across two genetically distinct switchgrass subpopulations and
eight common gardens. Purple represents individuals from the Midwest
genetic subpopulation, and pink individuals from the Gulf subpopulation;
map positions represent the original collection locations for the
genotypes, and shapes represent the ecotype of the genotype. Vertical
dashed lines indicate the summer solstice. Common gardens are arranged
in latitudinal order. (b) Phenotypic correlations between clonal
replicates planted at eight common gardens, within and between two
genetic subpopulations. (c) Narrow sense heritability of green-up and
flowering within single common gardens (purple) and across all eight
common gardens (green), within and between two genetic subpopulations.
(d) Flow diagram of the methods applied to the green-up and flowering
dates to jointly estimate SNP effects across all sites. \emph{Mash} was
fit to SNP effect data and used to find covariance matrices that
improved the \emph{mash} model likelihood using a large set of randomly
selected, relatively unlinked SNP effects; this model was applied to a
``strong'' set of SNP effects with large effect sizes in the univariate
GWAS.}

@@

\caption{\label{fig-covar}Example hypothesis-driven covariance matrices
specified in \emph{mash} and the posterior weights placed on all
covariance matrices. (a) Left column: Five example hypothesized
covariance matrices specified for the green-up date or flowering date
phenotype; these matrices were created from environment-specific
correlations across eight common gardens, and are described in Table 1.
Common gardens are arranged in latitudinal order within the matrices.
Right column: Five example canonical covariance matrices. Canonical
matrices (purple) have simple interpretations, such as equal effects
across all common gardens, or effects specific to a single common
garden. (b,d) Total posterior weight placed on each covariance matrix
type specified for (b) green-up date and (d) flowering date \emph{mash}
models, within and between two genetic subpopulations. Hypothesized
covariance matrices (green). Covariance matrices included in \emph{mash}
that had zero posterior weight in all three \emph{mash} runs on the
genetic subpopulations, such as the identity matrix, are not shown.
(c,e) Total posterior weight placed on covariance matrices that were
hypothesized or canonical, for the (c) green-up date phenotype and (e)
flowering date phenotype.}

@@

\caption{\label{fig-qtl}Overlaps of QTL from an outbred pseudo-F2 cross
and with jointly re-estimated SNP effects in the 1\% tail of
significance from a diversity panel. Dotted lines indicate
permutation-based significance thresholds for each weather-related
function. Stars indicate QTL with significant enrichment for SNPs in the
1\% \emph{mash} tail; G, M, and B indicate which subpopulation had
enrichment: G - Gulf subpopulation, M -Midwest subpopulation, B - both
subpopulations. Rug plots show genomic locations of SNPs in the 1\%
\emph{mash} tail for flowering date for each subpopulation. a) QTL
mapping for the start of vegetative growth (Greenup Date), and three
weather-related functions of greenup date. b) QTL mapping for the start
of reproductive growth (Flowering Date), and two weather-related
functions of flowering date.}

@@

The formation and resequencing of the diversity panel has been described
previously (33). The diversity panel contained 134 sequenced, clonally
propagated individuals from the Midwest genetic subpopulation, and 229
from the Gulf genetic subpopulation. To allow for the possibility that
different subpopulations had different strengths of connection between
our phenotypes and genotypes (41), we conducted three sets of genetic
analyses: on Gulf and Midwest genotypes separately, and on both
subpopulations together (`Both' subpopulations). Analyses to determine
narrow-sense heritability (h\textsuperscript{2}) for green-up and
flowering were done using linear mixed models and followed (33). Details
on these models can be found in (SI Appendix, Section S2).

@@

To evaluate the prevalence and kinds of covariance patterns of SNP
effects across our common gardens, we used multivariate adaptive
shrinkage (\emph{mash}) on SNP effect estimates from the diversity panel
(36). To do this, we first conducted univarate genome-wide association
(GWAS) on site-specific best linear unbiased predictors (BLUPs) for the
timing of vegetative growth and flowering, using the switchgrassGWAS
package and the methods in (40). We used the effect estimates for single
nucleotide polymorphisms (SNPs) from these GWAS as preliminary effect
estimates for the two traits at each garden. We then jointly modeled
genetic effect estimates, and the mixture of ways these effects might
covary, across all eight common gardens, using a two-part procedure. We
first modeled genetic effects with different combinations of covariance
structures, using the effect size estimates from a subset of \ul{19K}
relatively unlinked (r\textsuperscript{2} \textless{} 0.2), randomly
selected SNPs used in the GWAS. In these models (hereafter referred to
as ``random''), we then specified a variety of potential covariance
structures among genetic effect size estimates from each garden (as
expanded on below) and used a greedy algorithm to iteratively select and
add covariance structures that significantly improved the log likelihood
of the \emph{mash} model. Details on these models can be found in (SI
Appendix, Section S3). Given the high correlation between some of the
covariance patterns we tested, this approach allowed us to select only
the subset of patterns of covariance that significantly improved the fit
of the jointly inferred structure of genetic effect estimates present in
the data. We then selected 19K relatively unlinked (r\textsuperscript{2}
\textless{} 0.2) SNPs from each univariate GWAS that had the largest
effect estimates in each GWAS (hereafter ``strong'' effects), which gave
sets of \ul{\textbf{48K - 80K}} SNPs, and jointly re-estimated these
effect size estimates at all eight sites using the set of significant
covariance matrices that most improved the model fit on the random
effects. Notably, the majority of these ``strong'' effects were not
significant in univariate GWAS.

We generated hypothesis-based covariance matrices derived from
correlations in environmental cues in the green-up or flowering date
windows for the three populations (Table 1; SI Appendix, Table S1,
Section S1). These covariance matrices represent correlations between
identical genotypes drawn from a specific population at pairs of common
gardens; covariances near one mean that the population has a strong,
positive linear relationship in individual responses at that pair of
gardens, while covariances near zero mean that there is no relationship
within the population for individual responses at that pair of gardens.
\emph{Mash} SNP effects will undergo strong shrinkage towards one
another in the first case, and little shrinkage in the second case.
\emph{Mash} also generates data-driven covariance matrices corresponding
to major patterns of SNP effects present in the data. We generated six
data-driven matrices per \emph{mash} run, five produced by singular
value decomposition (SVD) of an overall matrix.

@@

To confirm candidate genomic regions and patterns of allelic effects
found in the diversity panel, we analyzed flowering in an outbred
pseudo-F2 cross between four individuals, two Midwest and two Gulf
individuals. The formation of this mapping population has been described
previously (35); additional details on QTL mapping can be found in SI
Appendix, Section S4. To be directly comparable to the diversity panel
data, only 2019 phenology data from the pseudo-F2 cross from the same
eight common garden sites were used.
